### 2020-03-14 paper/main.tex
new work

   Committee Members: \\

@@

\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

@@

\mainmatter

\chapter{Introduction}

[explain what black box and white box is]
In this thesis, we study interpretable machine learning as applied to complex-valued time series. Scientists have studied the use of several machine learning methods such as Convolutional Neural Networks, Recurrent Neural Networks, and Support Vector Machines for time series classification.

[add more reasons]
[add how most time series are classified]
These methods, however, fall short of allowing users to visualize patterns within their dataset and ().

To address this issue, we propose an interpretable hybrid  model that can be extended to any time series dataset. Our architecture is composed of two models, an ensemble method of classifiers that functions as a black box method, and a white-box model that encodes time series as images, attemps to classify them through a CNN, and outputs all images correctly classified in both black-box and white-box method.

In our black-box model, we analyze  deep learning models such as CNN’s which have become increasingly popular and widely used in the last decade but their complex nature makes it difficult for users to understand what is going on. So, as black-box models get more popular the need for an interpretable accessory? is needed so we propose a hybrid model consisting of a black box for classification and an interpretable white-box model which highlights characteristics of a time series for users to understand.

\section{The need for interpretable models in management problems}
The growth of mobile devices and demand for wireless data has created a need for igh quality spectrum sensing and adaptation to improve spectral allocation and interference mitigation is an important route by which we may achieve this.  however have been constrained to relatively specialized solutions which lack the generality needed to deal with a complex and growing number emitter types, interference types and propagation environments.
This is a significant challenge in the community as expert systems designed to perform well on specialized tasks often lack flexibility and can be expensive and tedious to develop analytically.

\section{Contributions}
[fill in]

\section{Data}

We analyzed our model on three radio signal datasets generated using Spatial Modulation. Spatial Modulation is a transmission technique that uses multiple antennas. It maps a block of information bits to two units, one is a symbol chosen from a constellation diagram, and the second one is a unique transmit antenna number that is chosen from a set of transmit antennas. The method in which transmit antennas send and receive radio waves can be described through polarization. Two popular basis polarizations are horizontal linear, H, and vertical linear, V. Our datasets contain data horizontally transmitted and vertically received (HV) and data vertically transmitted and vertically received.

The two properties HV and VV, are given to us in raw discrete format. Both properties are consist of time and amplitude values but vary in length and in how they are processed. The raw signal consists of over 31,000 data points with the exact time it was received. The size of the discrete data can vary from 22 to 44 data points, and is a processed representation of the raw signal that has equally spaced values.

[ What is raw signal and discrete, compare them, ]
[explain hv, vv]
\chapter{Preprocessing}
Radio signal data is presented in a complex-valued format that is unusable in a typical neural network, so in an attempt to make our model robust and reduce any complexity, we focused on using real values as features.

@@

\subsection{STFT/ FT}
% [Recall we can write a complex number in terms of its magnitude and phase
% (i.e., its polar representation). ]

% Transformation 1 : STFT/ FT
[what is it]

[fft formula]
The Fourier Transform (FT) is a mathematical tool that decomposes any function into a sum of sinusoidal basis functions. Each basis function is a complex value of a frequency, so it allows us to view our data in the frequency domain as opposed to amplitude.

One of the shortcomings of the FT is rooted in the Heisenberg Uncertainty Principle (HUP) [quote?]. The HUP states that the position and velocity of an object cannot be simultaneously measured, which can be applied to the time-frequency information of a signal. This means we cannot know which spectral components exist at any given time. The closest we can get is sampling at different ranges of time and finding a range of frequencies within that time frame. This method is described as the Short-Time Fourier Transform.

@@

\subsection{Shortcoming stft}
[stft]
The Short-Time Fourier transform (STFT) is a Fourier related transform used to determine the sinusoidal frequency and phase content of local sections of a signal as it changes over time.[Ref] 
Computing STF requires the signal to be divided into segments of equal length and then have the FT applied to that segment. This allows us to view the Fourier spectrum at a more granular level, which could potentially reveal different patterns amongst signals of different classes.

@@

@@

Transformation 2: Amplitude / Phase
The representation of a complex number as a sum of a real and imaginary number, z = x + iy, is called its Cartesian representation. For every cartesian point, we calculate its radius and angular distance which are real values and use those as features.

[purpose and motivation? Behind making it ang/abs]

[definition plus method]

\subsection{Transformation 2: Sliding window }

Transformation 2: Sliding window 
We propose a method similar to STFT but to reduce the size of the data we take the mean at each window which would turn our size into size N where N is equal to the number of windows we use.

@@

Wavelets are similar to the FT in which they deconstruct a signal using representations of other signals. The key difference is that wavelet signals are finite in time and frequency as opposed to sin and cos signals, which can carry on forever. This allows us to extract information from a signal with respect to time and location.

@@

We use spline interpolation in order to resize each level of decomposition into a single array. We tested different sizes of interpolation from N to N/3, where N is the size of the largest discrete signal size and found no reduction in performance.

\subsection{Each level}
Figure {X} depicts our model in which each level of decomposition is treated as its own dataset. We found no difference in accuracy compared to the resampling method.

\chapter{Models}
% [introduce models definitions]
% [EXPLAIN LOSS AND HOW ACCURACY IS MEASURED]

@@

Convolutional neural networks perform feature learning via non-linear transformations implemented as a series of layers. The input data is a multidimensional array, called a tensor. The input data is passed through an input layer, followed by a series of hidden layers to extract features, and finally, an output layer, which in the case of classification, gives a probability for each class.

@@

% [lstm]
Long short-term memory (LSTM) is an artificial recurrent neural network (RNN) architecture[1] used in the field of deep learning. Unlike standard feedforward neural networks, LSTM has feedback connections. It can not only process single data points (such as images), but also entire sequences of data (such as speech or video). For example, LSTM is applicable to tasks such as unsegmented, connected handwriting recognition[2], speech recognition[3][4] and anomaly detection in network traffic or IDS's (intrusion detection systems).

A common LSTM unit is composed of a cell, an input gate, an output gate and a forget gate. The cell remembers values over arbitrary time intervals and the three gates regulate the flow of information into and out of the cell.

LSTM networks are well-suited to classifying, processing and making predictions based on time series data, since there can be lags of unknown duration between important events in a time series. LSTMs were developed to deal with the exploding and vanishing gradient problems that can be encountered when training traditional RNNs. Relative insensitivity to gap length is an advantage of LSTM over RNNs, hidden Markov models and other sequence learning methods in numerous applications.

\subsection{multimodal}

[multimodal]
Due to the superior performance and computationally tractable representation capability (in vector spaces) in multiple domains such as visual, audio, and text, deep neural networks have gained tremendous popularity in multimodal learning tasks [38, 39, 44]. Typically, domain-specific neural networks are used on different modalities to generate their representations and the individual representations are merged or aggregated. Finally, the prediction is made on top of aggregated representation usually with another a neural network to capture the interactions between modalities and learn complex function mapping between input and output. Addition (or average) and concatenation are two common aggregation methods, i.e.,
The network structure is illustrated in Figure 1(b) . The arrows are function mappings or computing operations. The dotted boxes are representations of single and combined modality features. We call them additive combinations because their critical step is to add modality hidden vectors (although often in a nonlinear way).

[explain architectures]

@@

Our CNN architecture consists of 3 convolutional layers each followed by a batch normalization and dropout layer then finally connected to two dense layers (Figure X). We attempted to make it deeper but found inconsistent performance across all of our datasets.
[add figure]
\subsection{LSTM}
We wanted to keep our LSTM network as small as possible, for X purposes, so we went with two LSTM layers of 128 hidden states and a dropout rate of 4/10  followed by a dense layer of 128 connections. We attempted different state sizes but found 128 to be the smallest number with the best consistent performance.

[add figure]

\subsection{Final method}
We propose a multimodal learning architecture for the purpose of time series classification which is illustrated in Figure (X). The multimodal architecture allows our data to vary in size and given that all four levels of decomposition have varying length due to downsampling, we propose each model to learn the representation of each distinct feature. For this architecture we propose two models, a 1D CNN and an LSTM, in which we employ two CNN’s and 1 LSTM. They are all concatenated after their respective dense layer which performs the final   We tried numerous variations and saw no impact on performance. 
[add figure]

\section{mtf}

We approach our MTF is slightly different than  because instead of performing it over all samples in the dataset we perform it for every signal.

The three attributes we use are values are the absolute value of HV SBR, the absolute value of VV SBR, and a mathematical combination of the two (Figure X).

[add figure]

\section{Notation}

\section{Layout}

\chapter{Related Work}

\chapter{Markov Transition Fields}
We propose a framework similar to [] for encoding dynamical transition statistics,
but we continue their work by considering ith order Markov transition probabilities.
Given a time series X, we decompose its magnitude axis into two separate
properties by representing it as a polar coordinate, Xangular and Xradial. We then
identify the Q quantile bins for both properties and the temporal values Xtime
and assign each x in Xangular, Xradial, Xtime to its corresponding bin qj (j in
[1, Q]). Thus we construct three QxQ adjacency transition matrices, Wangular,
Wradial, Wtime, by counting transitions among quantile bins in the manner of a
ith order Markov chain along the time axis.

W does not take into account the temporal axis so to prevent any information
loss we construct a Markov Transition Field (MTF) for each W. The MTF
denotes the probability of transitioning from qi to qj for each x in X. This,
in turn, allows us to consider the transition probability on the magnitude and
temporal axis.

As described in [] the MTF encodes the multi-span transition probabilities
of the time series, but given that we have three different M’s we modify their
approach and consider each M to be a separate color channel of RGB where
Mangular is red, Mtime is blue, Mradial is green.

\chapter{Main Results}

\section{black box}
Our black-box model is constructed of four different architectures, 1 LSTM and 2 CNN’s, that are concatenated at the dense layer. The four features we use are amplitude/phase of each level of decomposition for HV and VV. We chose four because we wanted to take into consideration both HV / VV in the event that one had more descriptive features than the other. Figure {X} depicts our model.

@@

\section{10k data}
Given that this is much larger than our other data we split our data into 10\% training and 90\% test. We found no drop in performance nor in accuracy.

[add table for results]

\section{white box}
Our white box is composed of a model that takes in raw data as an input and converts each signal into an image through the MTF method. We then pass those images through a CNN and those that are correctly classified are shown to the user.

@@

[add results]

\chapter{Conclusion}
\label{chap:conclusion}

% \bibliography{../references/main}
% \bibliographystyle{plain}

>>>>

   Committee Members: \\
   Ju Cheol Moon, Ph.D \\
   Roman Tankelevich, Ph.D \\
   Seok-Chul Kwon, Ph.D

   College Designee: \\
   Hamid Rahai, Ph.D.

@@

\chapter*{Abstract}

% In this thesis, we study interpretable machine learning as applied to complex-valued time series data. Scientists have studied the use of several machine learning methods such as Convolutional Neural Networks, Recurrent Neural Networks, and Support Vector Machines for time series classification. These methods, however, fall short of allowing users to visualize patterns within their dataset.

% To address this issue, we propose an interpretable hybrid model that can be extended to any time series dataset. Our architecture is composed of two models, an ensemble method of classifiers that functions as a black-box method, and a white-box model that encodes time series as an image, attempts to classify them through a CNN, and outputs all images correctly classified in both black-box and white-box models.

\addcontentsline{toc}{chapter}{Abstract}
\chapter{Acknowledgments}

@@

\mainmatter
\chapter{Introduction}
\label{chap:introduction}

As time series datasets become ever so popular the need for deep learning models becomes greater.
In our black-box model, we analyze deep learning models such as CNN’s which have become increasingly popular and widely used in the last decade but their complex nature makes it difficult for users to understand what is going on \cite{wang_hybrid_2019}. So, as black-box models get more popular the need for an interpretable accessory is needed so we propose a hybrid model consisting of a black box for classification and an interpretable white-box model which highlights characteristics of a time series for users to understand.

% \section{The need for interpretable models in management problems}
% The growth of mobile devices and demand for wireless data has created a need for igh quality spectrum sensing and adaptation to improve spectral allocation and interference mitigation is an important route by which we may achieve this.  however have been constrained to relatively specialized solutions which lack the generality needed to deal with a complex and growing number emitter types, interference types and propagation environments.
% This is a significant challenge in the community as expert systems designed to perform well on specialized tasks often lack flexibility and can be expensive and tedious to develop analytically.

\section{Contributions}
We focus on creating deep learning architectures to classify our datasets as well as extending existing work to create our white-box model. Our final results show how robust our black-box method is as well as support for our white-box model.

\chapter{Data}

We analyzed our model on three radio signal datasets generated using Spatial Modulation. Spatial Modulation is a transmission technique that uses multiple antennas. It maps a block of information bits to two units, one is a symbol chosen from a constellation diagram, and the second one is a unique transmit antenna number that is chosen from a set of transmit antennas \cite{mesleh_spatial_2008}. The method in which transmit antennas send and receive radio waves can be described through polarization. Two popular basis polarizations are horizontal linear, H, and vertical linear, V. Our datasets contain data horizontally transmitted and vertically received (HV) and data vertically transmitted and vertically received.

The two properties HV and VV, are given to us in raw discrete format. Both properties consist of time and amplitude values but vary in length and in how they are processed. The raw signal consists of over 31,000 data points with the exact time it was received. The size of the discrete data can vary from 22 to 44 data points and is a processed representation of the raw signal that has equally spaced values. In this thesis we focus on discrete data given that it is closer to datasets in real-world situations.

% [ What is raw signal and discrete, compare them, ]
% [explain hv, vv]

\chapter{Related Work}
\label{chap:relatedwork}

\chapter{Preprocessing}
\label{chap:preprocessing}

Radio signal data is presented in a complex-valued format that is unusable in a typical neural network, so in an attempt to make our model robust and reduce any complexity, we focused on using real values as features.

@@

\subsection{Fourier Transform}
% [Recall we can write a complex number in terms of its magnitude and phase
% (i.e., its polar representation). ]

% Transformation 1 : STFT/ FT
% [what is it]

% [fft formula]
The Fourier Transform (FT) is a mathematical tool that decomposes any function into a sum of sinusoidal basis functions. Each basis function is a complex value of a frequency, so it allows us to view our data in the frequency domain as opposed to amplitude.

One of the shortcomings of the FT is rooted in the Heisenberg Uncertainty Principle (HUP) \cite{hill_uncertainty_nodate}.  The HUP states that the position and velocity of an object cannot be simultaneously measured, which can be applied to the time-frequency information of a signal. This means we cannot know which spectral components exist at any given time. The closest we can get is sampling at different ranges of time and finding a range of frequencies within that time frame. This method is described as the Short-Time Fourier Transform.

@@

\subsection{Short-Time Fourier Transform}
% [stft]
The Short-Time Fourier transform (STFT) is a Fourier related transform used to determine the sinusoidal frequency and phase content of local sections of a signal as it changes over time. \cite{hill_uncertainty_nodate}
Computing STF requires the signal to be divided into segments of equal length and then have the FT applied to that segment. This allows us to view the Fourier spectrum at a more granular level, which could potentially reveal different patterns amongst signals of different classes.

@@

% [purpose and motivation? Behind making it ang/abs]

% [definition plus method]

\subsection{Sliding Window Method}

We propose a method similar to STFT but to reduce the size of the data we take the mean at each window which would turn our size into size N where N is equal to the number of windows we use. This performed as well as STFT and gave us the advantage of reducing the dimensionality of our data.

@@

% Transformation 2: Amplitude / Phase
The representation of a complex number as a sum of a real and imaginary number, z = x + iy, is called its Cartesian representation. For every cartesian point, we calculate its radius and angular distance which are real values and use those as features. This method outperformed the previous three methods but limited our feature size which made it difficult to get consistent accuracy across all three of our datasets.

@@

Wavelets are similar to the FT in which they deconstruct a signal using representations of other signals. The key difference is that wavelet signals are finite in time and frequency as opposed to sin and cos signals, which can carry on forever \cite{strang_wavelets_1996}. This allows us to extract information from a signal with respect to time and location.

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.4]{../media/wavelet_families.png}
   \end{center}
   \caption{Example of different types of wavelets.}
   \label{fig:reinforcementAgent}
\end{figure}

@@

We use spline interpolation in order to resize each level of decomposition into a single array. We tested different sizes of interpolation from N to N/3, where N is the size of the largest discrete signal size, and found no reduction in performance.

\subsection{Each level}
Figure \ref{fig:multimodal_overview} depicts our model in which each level of decomposition is treated as its own dataset. We found no difference in accuracy compared to the resampling method. However, given that related work we found treated each decomposition level as its own dataset, we decided to go with this method.

\chapter{Models}
\label{chap:models}

% [introduce models definitions]
% [EXPLAIN LOSS AND HOW ACCURACY IS MEASURED]

@@

Convolutional Neural Networks perform feature learning via non-linear transformations implemented as a series of layers. The input data is a multidimensional array, called a tensor. The input data is passed through an input layer, followed by a series of hidden layers to extract features, and finally, an output layer, which in the case of classification, gives a probability for each class.

% create your own design
\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.3]{../media/nn_highlight.jpeg}
   \end{center}
   \caption{Example of a Convolutional Neural Network.}
   \label{fig:reinforcementAgent}
\end{figure}

@@

% [lstm]
Long short-term memory (LSTM) is an artificial recurrent neural network (RNN) architecture used in the field of deep learning. Unlike standard feedforward neural networks, LSTM has feedback connections. It can process not only single data points but also entire sequences of data.

A standard LSTM unit is composed of a cell, an input gate, an output gate, and a forget gate. The cell remembers values over arbitrary time intervals, and the three gates regulate the flow of information into and out of the cell.

LSTM networks are well-suited to classifying, processing, and making predictions based on time series data since there can be lags of unknown duration between significant events in a time series. LSTMs were developed to deal with the exploding and vanishing gradient problems that can be encountered when training traditional RNNs.

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.5]{../media/lstm_highlight.png}
   \end{center}
   \caption{Example of a LSTM unit.}
   \label{fig:reinforcementAgent}
\end{figure}

\subsection{Multimodal Deep Learning}

% [multimodal]
Due to the superior performance and computationally tractable representation capability in multiple domains such as visual, audio, and text, deep neural networks have gained tremendous popularity in multimodal learning tasks \cite{kim_multimodal_2018}. Typically, domain-specific neural networks are used on different modalities to generate their representations, and the individual representations are merged or aggregated. Finally, the prediction is made on top of aggregated representation, usually with another neural network to capture the interactions between modalities and learn complex function mapping between input and output.

% [explain architectures]

@@

Our CNN architecture consists of 3 convolutional layers each followed by a batch normalization and dropout layer then finally connected to two dense layers (Figure X). We attempted to make it deeper but found inconsistent performance across all of our datasets.
% [add figure]

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.6]{../media/cnn_model.png}
   \end{center}
   \caption{CNN architecture used in our black-box model.}  
    \label{fig:cnn_model}
\end{figure}

\subsection{LSTM}
We wanted to keep our LSTM network as small as possible, for X purposes, so we went with two LSTM layers of 128 hidden states and a dropout rate of 4/10  followed by a dense layer of 128 connections. We attempted different state sizes but found 128 to be the smallest number with the best consistent performance.

% [add figure]
\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.6]{../media/lstm_model.png}
   \end{center}
   \caption{LSTM architecture used in our black-box model.}
   \label{fig:lstm_model}
\end{figure}

\subsection{Final Model}

We propose a multimodal learning architecture for the purpose of time series classification which is illustrated in Figure \ref{fig:multimodal_overview}. The multimodal architecture allows our data to vary in size and given that all three levels of decomposition have varying length due to downsampling, we propose each model to learn the representation of each distinct feature. For this architecture we propose two architectures, a 1D CNN and an LSTM, in which we employ two CNN’s and 1 LSTM. They are all concatenated after their respective dense layer after which they perform classication via a softmax layer. 
% [add figure]

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.6]{../media/multimodal_overview.png}
   \end{center}
   \caption{Overview of our black-box model.}
   \label{fig:multimodal_overview}
\end{figure}

% \section{mtf}

% We approach our MTF is slightly different than  because instead of performing it over all samples in the dataset we perform it for every signal.

% The three attributes we use are values are the absolute value of HV SBR, the absolute value of VV SBR, and a mathematical combination of the two (Figure X).

% [add figure]

\chapter{Markov Transition Fields}
\label{chap:mtf}

% We propose a framework similar to [] for encoding dynamical transition statistics,
% but we continue their work by considering ith order Markov transition probabilities.
% Given a time series X, we decompose its magnitude axis into two separate
% properties by representing it as a polar coordinate, Xangular and Xradial. We then
% identify the Q quantile bins for both properties and the temporal values Xtime
% and assign each x in Xangular, Xradial, Xtime to its corresponding bin qj (j in
% [1, Q]). Thus we construct three QxQ adjacency transition matrices, Wangular,
% Wradial, Wtime, by counting transitions among quantile bins in the manner of a
% ith order Markov chain along the time axis.

% W does not take into account the temporal axis so to prevent any information
% loss we construct a Markov Transition Field (MTF) for each W. The MTF
% denotes the probability of transitioning from qi to qj for each x in X. This,
% in turn, allows us to consider the transition probability on the magnitude and
% temporal axis.

% As described in [] the MTF encodes the multi-span transition probabilities
% of the time series, but given that we have three different M’s we modify their
% approach and consider each M to be a separate color channel of RGB where
% Mangular is red, Mtime is blue, Mradial is green.

% \section{Markov Transition Field}

We propose a framework similar to \cite{wang_encoding_nodate}  for encoding dynamical transition statistics, but we continue their work by i\textsuperscript{th} order Markov transition probabilities.

Given a time series X, we decompose its magnitude axis into three separate properties, P\textsubscript{1},  P\textsubscript{2},  P\textsubscript{3}. We then identify the Q quantile bins for each property  and assign each $x \in P\textsubscript{1},  P\textsubscript{2},  P\textsubscript{3}$ to its corresponding bin q\textsubscript{j} (j in [1, Q]). Thus, we construct three QxQ adjacency transition matrices, W\textsubscript{1}, W\textsubscript{2}, W\textsubscript{3}, by counting transitions among quantile bins in the manner of a i\textsuperscript{th} order Markov chain along the time axis.

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.6]{../media/mtf_q.png}
   \end{center}
   \caption{Example of QxQ quantile bin matrix used to calculate MTF.}
   \label{fig:mtf_q}
\end{figure}

%summation %. This effectively removes any sensitivity to the X’s distribution and temporal dependency to each time step t i. To account for any information loss after removing the temporal dependency, we follow the same approach as \cite{wang} and construct a Markov Transition Field for each property like so: %some figure%

W does not take into account the temporal axis so to prevent any information loss we construct a Markov Transition Field, M, for each W. The MTF denotes the probability of transitioning from q\textsubscript{i} to q\textsubscript{j} for each $x \in P$. This, in turn, allows us to consider the transition probability on the magnitude and temporal axis.

\begin{figure}[h]
  \centering
  M =
  \[\begin{bmatrix}

  \text{W\textsubscript{ij}} | \text{$x\textsubscript{1} \in q\textsubscript{i}$, $x_{1} \in q\textsubscript{j}$}
  & \dots &

  \text{W\textsubscript{ij}}  |  \text{$x_{1} \in q\textsubscript{i}$, $x_{n} \in q\textsubscript{j}$}

  \\

  \vdots &  \ddots & \\

  \text{W\textsubscript{ij}} | \text{$x_{n} \in q\textsubscript{i}$, $x_{1} \in q\textsubscript{j}$}
  & \dots &
  \text{W\textsubscript{ij}} | \text{$x_{n} \in q\textsubscript{i}$, $x_{n} \in q\textsubscript{j}$} \\

  \end{bmatrix}\]
  \caption{Markov Transition Field where  W\textsubscript{ij} denotes the transition probability from quantile i to j.}
  \label{fig:mtf}
\end{figure}

As described in \cite{wang_encoding_nodate} the MTF encodes the multi-span transition probabilities of the time series, but given that we have three different M's we modify their approach and consider each M to be a separate color channel of RGB where M\textsubscript{1} is red, M\textsubscript{2} is blue, M\textsubscript{3} is green. Since each row in M is a probability from 0 to 1 we multiply it by 255 to get a color value.

\chapter{Main Results}
\label{chap:results}

\section{Black-Box Model}
Our black-box model is constructed of three different architectures, 1 LSTM and 2 CNN’s, that are concatenated at the dense layer. The three features we use are amplitude/phase of each level of decomposition for HV and VV. We chose four because we wanted to take into consideration both HV / VV in the event that one had more descriptive features than the other.

@@

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=0.6]{../media/results.png}
   \end{center}
   \caption{Results}
   \label{fig:final_results}
\end{figure}

\section{Dataset B}

Given that this dataset is ten times larget than our other two datasets we wanted to try different training and test splits, namely we went as low as 8\% for training data and used the remaining 92\% as test data. We ran the same number of cross validation as our previous tests and found minimal difference in performance.

% [add table for results]

\section{White-Box Model}
Our white box is composed of a model that takes in raw data as an input and converts each signal into an image through the MTF method. We then pass those images through a CNN and those that are correctly classified are shown to the user.

@@

\begin{figure}[h!]
   \begin{center}
      \includegraphics[scale=.7]{../media/alexnet.png}
   \end{center}
   \caption{CNN architecture for classifying images generated through MTF's.}
   \label{fig:mtf_cnn_results}
\end{figure}

% [add results]

\chapter{Conclusion}
\label{chap:conclusion}
Throughout this thesis, we have stressed the importance of a hybrid machine learning algorithm as well as providing a framework that can successfully classify and visualize different classes when applied to time-series data.

We proposed an extension to existing work described in [] so users can visualize their data while being able to classify them with 60\% accuracy on our dataset and model. We also created a robust black-box model consisting of two different deep learning architectures that consistently provided competitive accuracy.

In the future, we would like to explore other methods for our white-box model that would act as an alternative to Markov Transition Fields in hopes that it produces higher accuracy than our current model. Additionally, we would like to extensively test our model on different time-series datasets, not just radio signal datasets.

\bibliography{../references/main}
\bibliographystyle{plain}
